Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2020-01-21 acks.tex
Second round

>>>>

I also want to thank my PhD colleagues for their friendship, in particular
Tillmann, Sebastian and Jonathan Brachthäuser, who helped make the challenges of
research less solitary.

Most importantly, thanks to my late mother Rosalia, who sadly passed near the end of my
PhD. I've struggled to thank her properly in this thesis, but I just can't; I'll
just say I'm thankful for all she did for me, and she's behind everything I am.

Finally, I'll thank my family and friends for all their support and
entertainment: unfortunately, they are too many to list here, and I'd surely
forget somebody who deserves to be listed, but they already know what I'd write
here.
